---
title: "subject filtering"
author: Azeez Adebimpe 
output: html_notebook
---

This sample was selected from [ Marieta work with NMF application on  T1w images ](https://github.com/PennBBL/pehlivanovaPncItcScripts). A total *452 subjects* were used for her final analysis. Those subjects were screen furteher fore resting state analysis,

1. Merge the Resting state QA with Marieta subjects to select subjects with both T1w and resting state data 

```{r}
restdatapnc=read.csv('~/Box/projects/ITC/demographics/n2416_RestQAData_20170714.csv') # pnc QA
nmel=read.csv('~/Box/projects/ITC/demographics/n452_pnc_itc_whole_sample_20160825.csv') # Marieta subbjecct 
pncitc=merge(nmel,restdatapnc,by=c('bblid','scanid')) # select ids for  
```



2. select covariates (logk,age,sex,race, motion etc ) and subjects that pass resting-state QA (motion and voxelwise)
```{r}
pncit1 <- data.frame(
  pncitc$bblid,
  pncitc$scanid,pncitc$logk,pncitc$ageAtScan,pncitc$logAlpha,pncitc$sex,pncitc$race,pncitc$race2,pncitc$restExclude,pncitc$restExcludeVoxelwise,
  pncitc$restNoDataExclude,pncitc$relMeanRMSmotion,pncitc$restNSpikesMotion,pncitc$restNSpikesMotionExclude,pncitc$restRelMeanRMSMotionExclude
)

colnames(pncit1)=c('bblid',
                   'scanid','logk','ageAtScan','logAlpha','sex','race','race2','restExclude','restExcludeVoxelwise',
                   'restNoDataExclude','relMeanRMSmotion','restNSpikesMotion','restNSpikesMotionExclude','restRelMeanRMSMotionExclude')

pncit1=pncit1[which(pncit1$restExcludeVoxelwise==0),]
pncit1=pncit1[which(pncit1$restRelMeanRMSMotionExclude==0),]
pncit1=pncit1[-which(is.na(pncit1$relMeanRMSmotion)),]
```


3. 308 subjects were good but one subject (bblid 96832) has 96 timepoints instead of 120

```{r}
pncit1=pncit1[-which(pncit1$bblid==96832),]
ids=data.frame(pncit1$bblid,pncit1$scanid) # get bblid and scanid for futher analyis 
write.csv(ids,'~/Box/projects/ITC/newscript/n307_blbid_scanid.csv',row.names = FALSE,quote = FALSE)
pncit1$age=pncit1$ageAtScan/12
write.csv(pncit1,'~/Box/projects/ITC/newscript/n307_demographics.csv',row.names = FALSE,quote = FALSE)

```



