---
title: "CWASMDR"
author: Azeez Adebimpe
output: html_notebook
---


operation directory: CBICA :*/cbica/projects/GURLAB/projects/pncitc*
## 1. demo
 The 307 subjects resting state data were selected from data freeze. The data were downsampled to from 2mm to 4mm. the data is in PNC space. 
This script (*downsampleniftito4mm.sh*) was used to get the data into 4mm for *cwasmdmr*

## 2. Running CWASMDMR. 
 It requires greymatter mask and background image, both in 4mm and same space as object
 a. greymattermask:PNCgrey.nii.gz  
 b. bgimage : PNCbrain.nii.gz
 c. imagelist: imageinput_rest.csv 
 
 Greymatter mask and bgimage are obtained  from PNC template. 
 
 Image inputs  is arranged as it appear on the ids list (*n307_blbid_scanid.csv*) and demographic (*n307_demographic.csv*)
 
 The cwasmdmr first step is to compute the *distance matrix*  between subjects with this script: **cwas_pearson.sh**
 **cwas_pearson.sh**
 
  The second step is *MDMR*. The distance matrix is used as dependent variable and motion,sex, age and logk as the main factor: 
  
    $ distancematrix = logk+relMeanRMSmotion+sex+age $
  
  All covraiates are in *n307_demographic.csv* and **logk_motion_sex_age.sh** script was used to run the 
  *MDMR* 
  
  
## 3. Identify the clusters from the mdmr output
The cluster analysis was ran with the script **grf_fslcluster.sh**, written based on  [FSL cluster analysis](https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/Cluster) with  Gaussian Random Field (GRF) theory. 

The cluster analysis as shown below as shown below: 

   ```
   dir1=/cbica/projects/GURLAB/projects/pncitc
  grf_fslcluster.sh -i ${dir1}/output/cwas307/logk_motion_sex_age2/zstats_logk.nii.gz  \ # zstats dfrom mdmr
   -m ${dir1}//output/cwas307/mask.nii.gz \ # mask 
   -t 3.09 \ # high threshold 
    -o ${dir}/output/cwas  # output directory 
    
   ```
The output is in **${dir}/output/cluster_Z3.09** 
two significant clusters was found at frontal and TPJ regions: 


The clusters were separated and upsampled from 4mm to  2mm standard PNC template. 

```
/cbica/projects/GURLAB/projects/pncitc/output/cluster_Z3.09/mask1_2mm.nii.gz 
/cbica/projects/GURLAB/projects/pncitc/output/cluster_Z3.09/mask2_2mm.nii.gz 
```

Seed-based connectivity with xcpengine utility seed correlation with this script *seedcorrelation.sh*
### FLAMEO- Linear regression

make design matrix,group etc


```{r}
library(pracma)
demogr=read.csv('~/Box/projects/ITC/newscript/n307_demographics.csv')
#logk+relMeanRMSmotion+age 
desigmatlogkonly=cbind(rep(1,307),demogr$logk,demogr$relMeanRMSmotion,demogr$age)

#logk*age+relMeanRMSmotion+sex logk*age interaction 
designmatlogkage=cbind(rep(1,307),demogr$logk*demogr$age,demogr$relMeanRMSmotion)

#logk*sex+relMeanRMSmotion+age logk*sex interaction 
#designmatlogksex=cbind(rep(1,307),demogr$logk*demogr$sex,demogr$relMeanRMSmotion,demogr$age)

grp=ones(307,1)
contrast3=zeros(3,3); contrast4=zeros(4,4)
diag(contrast4)=1; diag(contrast3)=1

write.table(desigmatlogkonly,'~/Box/projects/ITC/newscript/desigmatlogkonly.txt',sep=' ',quote = FALSE,row.names = FALSE,col.names = FALSE)
write.table(designmatlogkage,'~/Box/projects/ITC/newscript/designmatlogkage.txt',sep=' ',quote = FALSE,row.names = FALSE,col.names = FALSE)
#write.table(designmatlogksex,'~/Box/projects/ITC/newscript/designmatlogksex.txt',sep=' ',quote = FALSE,row.names = FALSE,col.names = FALSE)
write.table(contrast3,'~/Box/projects/ITC/newscript/contrast3.txt',sep=' ',quote = FALSE,row.names = FALSE,col.names = FALSE)
write.table(contrast4,'~/Box/projects/ITC/newscript/contrast4.txt',sep=' ',quote = FALSE,row.names = FALSE,col.names = FALSE)
write.table(grp,'~/Box/projects/ITC/newscript/grp.txt',sep=' ',quote = FALSE,row.names = FALSE,col.names = FALSE)

```


The flameo ran  on CBICA
flameo ran with this script *flameo.sh* 

#### FDR  correction on flameo-output


```{r}
library(RNifti)
fmdir='/Users/adebimpe/Box/projects/pncitc/output/mask1/logk/'
mask=readNifti(paste0(fmdir,'mask.nii.gz'))
zz=c('zstat1','zstat2','zstat3','zstat4','zstat5')

for (i in 1:5 ){
z1=readNifti(paste0(fmdir,zz[i],'.nii.gz'))
Z=z1[mask==1]
p <- 2*pnorm((-abs(Z)))
p1=p.adjust(p, method = 'fdr')
zvals = qnorm(1 - (p1/2)) 
zvals[zvals==Inf]=10; Z[Z>0]=1; Z[Z<0]=-1
zm=mask
zm[mask==1]=zvals*Z
writeNifti(zm,paste0(fmdir,zz[i],'fdr.nii.gz'),template = mask) }

fmdir='/Users/adebimpe/Box/projects/pncitc/output/mask1/logkage/'
mask=readNifti(paste0(fmdir,'mask.nii.gz'))
zz=c('zstat1','zstat2','zstat3','zstat4')

for (i in 1:4 ){
z1=readNifti(paste0(fmdir,zz[i],'.nii.gz'))
Z=z1[mask==1]
p <- 2*pnorm((-abs(Z)))
p1=p.adjust(p, method = 'fdr')
zvals = qnorm(1 - (p1/2)) 
zvals[zvals==Inf]=10; Z[Z>0]=1; Z[Z<0]=-1
zm=mask
zm[mask==1]=zvals*Z
writeNifti(zm,paste0(fmdir,zz[i],'fdr.nii.gz'),template = mask) }

fmdir='/Users/adebimpe/Box/projects/pncitc/output/mask1/logksex/'
mask=readNifti(paste0(fmdir,'mask.nii.gz'))
zz=c('zstat1','zstat2','zstat3','zstat4')

for (i in 1:4 ){
z1=readNifti(paste0(fmdir,zz[i],'.nii.gz'))
Z=z1[mask==1]
p <- 2*pnorm((-abs(Z)))
p1=p.adjust(p, method = 'fdr')
zvals = qnorm(1 - (p1/2)) 
zvals[zvals==Inf]=10; Z[Z>0]=1; Z[Z<0]=-1
zm=mask
zm[mask==1]=zvals*Z
writeNifti(zm,paste0(fmdir,zz[i],'fdr.nii.gz'),template = mask) }

fmdir='/Users/adebimpe/Box/projects/pncitc/output/mask2/logk/'
mask=readNifti(paste0(fmdir,'mask.nii.gz'))
zz=c('zstat1','zstat2','zstat3','zstat4','zstat5')

for (i in 1:5 ){
z1=readNifti(paste0(fmdir,zz[i],'.nii.gz'))
Z=z1[mask==1]
p <- 2*pnorm((-abs(Z)))
p1=p.adjust(p, method = 'fdr')
zvals = qnorm(1 - (p1/2)) 
zvals[zvals==Inf]=10; Z[Z>0]=1; Z[Z<0]=-1
zm=mask
zm[mask==1]=zvals*Z
writeNifti(zm,paste0(fmdir,zz[i],'fdr.nii.gz'),template = mask) }

fmdir='/Users/adebimpe/Box/projects/pncitc/output/mask2/logkage/'
mask=readNifti(paste0(fmdir,'mask.nii.gz'))
zz=c('zstat1','zstat2','zstat3','zstat4')

for (i in 1:4 ){
z1=readNifti(paste0(fmdir,zz[i],'.nii.gz'))
Z=z1[mask==1]
p <- 2*pnorm((-abs(Z)))
p1=p.adjust(p, method = 'fdr')
zvals = qnorm(1 - (p1/2)) 
zvals[zvals==Inf]=10; Z[Z>0]=1; Z[Z<0]=-1
zm=mask
zm[mask==1]=zvals*Z
writeNifti(zm,paste0(fmdir,zz[i],'fdr.nii.gz'),template = mask) }

fmdir='/Users/adebimpe/Box/projects/pncitc/output/mask2/logksex/'
mask=readNifti(paste0(fmdir,'mask.nii.gz'))
zz=c('zstat1','zstat2','zstat3','zstat4')

for (i in 1:4 ){
z1=readNifti(paste0(fmdir,zz[i],'.nii.gz'))
Z=z1[mask==1]
p <- 2*pnorm((-abs(Z)))
p1=p.adjust(p, method = 'fdr')
zvals = qnorm(1 - (p1/2)) 
zvals[zvals==Inf]=10; Z[Z>0]=1; Z[Z<0]=-1
zm=mask
zm[mask==1]=zvals*Z
writeNifti(zm,paste0(fmdir,zz[i],'fdr.nii.gz'),template = mask) }

```


